\bgroup

\begin{TextWithEndnotes}

\chapter[Mind Bologna]{\texorpdfstring{Mind Bologna \endnote{I remember a guy in high school named Lance that used to have an expression "Mind bologna!" to refer to one's self being mind blown.}}{Mind Bologna }}

I am once again engulfed in the flames of literary masochism.\endnote{``Literary masochism'' is what I refers to furthering one's literary achievement to the detriment of one's self.}

I am once again drowning in melancholia.\endnote{I am diagnosed with Bipolar 1 Disorder.}

I am once again yearning for her.\endnote{D******}

To feel the tedium of daily life, or to feel the fire of bottomless hell that is my mind.\endnote{I forgot what this means, but it ties to the next line.}

``O, how I long to not be mediocre and to burn slowly and gracefully in front of everyone.''\endnote{I do not want to be a nobody. I do not want to die as a boring, lonesome being. I want to die beautiful. I want to die famous. I want to be known, even if that means suffering like hell on earth.}

\emph{What a fool! What a shameless masochist. Parading your suffering like some freak in an old town carnival. What an absolute fool!}\endnote{This is my rational mind preventing me from doing such things. This is the rational side of me that is preventing me from posting this poem to places where it can be used against me, or her. But I do not want to be a nobody. I want everybody to know my pain. I want to be famous at the expense of suffering.}

Although, perhaps, someone will come and calm this torrential hellstorm. Maybe.\endnote{She did come. She is my girlfriend, well, at least, at the time of writing. This is referencing the line that I wrote which reads ``She is the stillness in my torrential storm. I am the motion in her calm waters.''}

Maybe someone will come and disturb the stillness in the eye of the storm.\endnote{Foreshadowing oooooooh\ldots{}}

Maybe someone did come and disturbed the peace.\endnote{D******}

Additional motion in an already uneasy cyclone of gasoline.\endnote{I am extremely unstable. Anything that can topple over this veneer of stability will easily do so.}

Agitation. Confusion. Irritation.\endnote{Classic signs of a mixed state episode in Bipolar. However, it is exacerbated by the situation.}

{\LARGE WHAT THE FUCK DO YOU WANT}\endnote{When I was really pissed off with her, I texted her ``WHAT THE FUCK DO YOU WANT''}

\ldots{}\endnote{A break from the irrational mind, for the rational mind to come in to soothe the restless. But perhaps, it will as well go mad. I mean, who wouldn't from this shitty situation. Really, who wouldn't?}

\pagebreak

Please rest easy, restless thinker.\endnote{This is me soothing the restless mind locked up inside my skull.} Fret not, apricot.\endnote{This is the start of a shitty rhyme. This is me telling myself to not worry.}\endnote{Despite all of that, I still get to joke about shit.} But rot, not ``lets knot this knot'' will dot the plot.\endnote{This means that the end of the relationship with her will be rot. We will drift away from each other. There won't be a happy ending together with her. It will all end in rot, decay, unhappiness. A lot of unresolved ``could be''s.} Blot the lot.\endnote{I tainted the canvas of our relationship in a bad way. I fucked up every turn. I was the one who started this shit with her. I was the one who invited her to talk with me sexually. I was the one who asked her ``What about antidepressants? You cant cum with 'em?'' I was the one who first asked her to do horny shit with me. I was always the first one\ldots{}} Shot my shot, but left to rot.\endnote{I TOLD HER SO MANY TIMES THAT I \textbf{\emph{MIGHT}} LOVE HER ROMANTICALLY BUT SHE SHOT ME DOWN SO MANY TIMES BRUHHH} Got caught.\endnote{I was caught in this mess. We were both caught---NAY, more like we busted our ass and told multiple people about this bullshit, even to her FUCKING UNDERAGE SISTER?!?!?!?!?!?} Fought.\endnote{We fought a lot of times.} Wrought.\endnote{We forgave each other and bonded once more.} Drought.\endnote{I'm readying myself for it to go dry and end in decay.} AND NOW I WROTE THIS FUCKING THOUGHT.\endnote{What the fuck did I just wrote??? This is an outrage! I used her as a fuel for my literary masochism. Why is it so terse, yet so emotionally charged. Nobody even got what anything in this line means, before I wrote a concrete footnotes. How funny.}

``Im tired.''\endnote{After a full-blown maniacal outrage, I often times feel oddly soothed and tired. The outburst just before this line was an especially intense one. And thus, the fictional character that is supposedly mimicking me is now tired.}

Alright, let me sing you a lullabye.\endnote{Instead of entertaining my horny ass, she sang me a lullabye in orded to make me sleep.} Good night, parasite.\endnote{The parasite is my restless mind; my mental illness; the hypersexuality symptom in bipolar; the bad parts of me.} Don't let the bed mites bite.\endnote{Despite all of that, I still get to joke about shit.}

\end{TextWithEndnotes}

\egroup