\bgroup

\begin{TextWithEndnotes}

\chapter[Swing By Often Times]{\texorpdfstring{Swing By Often Times \endnote{This refers to my bipolar disorder that comes with extreme mood swings. It is a word play on the phrase ``come by sometime.'' ``Swing by often times'' also refers to my plea for help to other people to come by and listen to every worry I have.}}{Swing By Often Times}}

\centering

\textbf{\emph{Sleepy.}}

Dissapointed yet calm

Tired yet wakeful

\textbf{\emph{Frustrated.}}

Sedated yet restless

Medicated yet no improvement

I am going mad. I am going mad. I AM GOING MAD!

The thoughts won't stop. The words overflowing and can't be contained.

Alright, let me see you tap and clap. Non-stop hop and plop.\endnote{``Hop'' as in jump out of seat and do whatever to soothe this restless soul, then plopping my butt back the seat ad nauseam.} Flop this rap; scrap that.\endnote{This is a shitty poem. Someone described this part where the words breakdown into a shitty rhyme as an ``Eminem rhyme scheme.''} Open shop, then flop or drop.\endnote{I often come up with crazy, unvalidated business ideas that I often recruit and involve other people on. Which then turns into an embarassing turn of events when what I promised to them and my prospective clients could not be met.} Pop top up, unwrap, then write up.\endnote{It refers to ``popping the top of my skull up,'' as in to open up my feelings, often to the world, to then write about my feelings.} Snap then slap, then mop up the drop.\endnote{I often get so angry that I just snap and hurt somebody. Then I have to clean up the mess that I made. Often times, the attempt to fix things up will only worsen the situation.} Mishap then nap, stuck in a trap.\endnote{I abuse medication a lot. I drink meds that I am not supposed to drink. In a confession that I did to my doctors, I told them that I wanted to induce a coma, just so that my mood will regulate over the span of few days. But I have controlled myself by only taking a few medications that has sedated me for 18 hours.} Fap fap and fucking fap.\endnote{Endless masturbation. Nymphomania and hypersexuality brought to yours truly by mania.} \emph{And, oh crap!} IT WOULD NOT STOP!

{\LARGE THIS IS MADNESS!!!}

\ldots{}

\justifying

``Hey, here's a magic pill for you. It will cure all of your bad parts.''\endnote{I was recently prescribed with Cariprazine.}

\emph{Even me being a bad person?}

``Sure!''\endnote{Like a Christian, I was promised the promised land. I was promised a time where I would be stable. Where I would be normal again.}

So when? When does it kick in?

Dude, sedatives kick in 5 minutes after taking 'em

So where's the magic gone?

\centering

\textbf{\emph{Impatient.}}

When?

When do I get to sleep?

When can I feel normal again?

When do I get to feel okay?

WAHAHAHAHAHAHAHAHAHAHAHAHAHAHAHAHAHAHAHAHA

make it stop, please

please\ldots{}

\end{TextWithEndnotes}

\egroup